Homelessness in Toronto: A Solvable Social Issue

### 2023-04-20 outputs/paper/paper.qmd
spelling error
delete paragraph

The data used in the report is obtained from OpenDataToronto and the data set is called "Toronto Shelter System Flow.” It provides information on folks have been ‘actively homeless’ in the City of Toronto and accessing overnight services between 2019 and 2023. The data is organized using six different population groups. The dataset is used and explained to provide further analysis. Visualizations in graphs and tables are presented to illustrate the correlation between year, homelessness, category, age, and race. By data visualization and before constructing the model, we assumed the total population of actively homeless people over the past five years would be experiencing a steep rise. We present a multiple linear regression model to justify the relationship between homelessness and year. The interpretation of the final model and reasoning is shown in the latter section. A discussion is carried out and the the implications of the findings, including causes and solutions. We conclude with the following steps that need to be taken for a better future.

@@

## Government Lack of Spending

John Tory has recognized that the Government isn't spending enough money to support homelessness. Homelessness needs to be declared as a public emergency. The city stated on their website "Higher rates of illness and premature death among the homeless population have been widely recognized". Our hospitals are seeing a rise cold-related injuries due to Toronto's miserable winters. The Council of Toronto was proposed to approve accessible 24-hour, drop-in, and indoor spaces. They proceeded to reject this proposition because it would cost the city $400,000 a month per center to operate. It's unfair to the City to judge how they spend their money but when they add an extra $50,000,000 to the police budget but neglect the cities most vunreable people. It's also cheeky to note they spent $2,000,000 clearing out emcampents even though they created this.  Warming centers aren't the solution as death rates are still high but they're still critical to helping the homeless community.

>>>>

The data used in the report is obtained from OpenDataToronto and the data set is called "Toronto Shelter System Flow.” It provides information on folks have been ‘actively homeless’ in the City of Toronto and accessing overnight services between 2019 and 2023. The data is organized using six different population groups. The dataset is used and explained to provide further analysis. Visualizations in graphs and tables are presented to illustrate the correlation between year, homelessness, category, age, and gender. By data visualization and before constructing the model, we assumed the total population of actively homeless people over the past five years would be experiencing a steep rise. We present a multiple linear regression model to justify the relationship between homelessness and year. The interpretation of the final model and reasoning is shown in the latter section. A discussion is carried out and the the implications of the findings, including causes and solutions. We conclude with the following steps that need to be taken for a better future.

@@
